### 2016-01-27 paper/main.tex
add conversion of png files to make files more manageable size

Our {\tt R} package implementation typically takes about $~20$ seconds on a modern laptop for $p=100,000$, and scales linearly with $J$.

@@

\begin{figure} 
\begin{center}
\begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{../analysis/figure/plot_egdens.Rmd/scenario_density-1.pdf} 
	\caption{Densities of non-zero effects, $g_1$, used in simulations.} \label{fig:altdens}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_pi0est.Rmd/plot_pi0est-1.pdf} 
\caption{Comparison of true and estimated values of $\pi_0$. When the UA holds all methods yield conservative (over-)estimates for $\pi_0$, with \ashr being least conservative, and hence most accurate. When the UA does not hold (``bimodal" scenario) the \ashr estimates are slightly anti-conservative.} \label{fig:pi0sims}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfdr-1.pdf} 
\caption{Comparison of true and estimated $\lfdr$ from \ashr (ash.n). Black line is $y=x$ and red line is $y=2x$. Estimates of $\lfdr$ are conservative when UA holds, due to conservative estimates of $\pi_0$.} \label{fig:lfdr}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr-1.pdf} 
\caption{As in c), but for $\lfsr$ instead of $\lfdr$. Estimates of $\lfsr$ are consistently less conservative than $\lfdr$ when UA holds, and also less anti-conservative in bimodal scenario.}  \label{fig:lfsr}
\end{subfigure}
\end{center}
\caption{Results of simulation studies (constant precision $s_j=1$).}
\end{figure}

@@

Note that, compared with previous debates regarding testing, 
this section advances an additional reason for focussing on the sign of the effect, rather than just testing whether it is 0. 
In previous debates authors have argued against testing whether an effect is 0
because it is {\it implausible that effects are exactly 0}. Here we add that {\it even if one believes
that some effects may be exactly zero}, it is still better to focus on the sign, because generally {\it the data are more informative about that question}
and so inferences are more robust to, say, the inevitable mis-estimation of $\pi_0$.
To provide some intuition, consider an observation with a $z$ score of 0. The $\lfdr$ of this observation can range from 0 (if $\pi_0=0$)
to 1 (if $\pi_0=1$). But, assuming a symmetric $g$, the $\lfsr>0.5$ whatever the value of $\pi_0$, because the observation $z=0$ says
nothing about the sign of the effect.
Thus, are two reasons to use the $\lfsr$ instead of the $\lfdr$: it answers a question that is more generally meaningful (e.g. it applies
whether or not zero effects truly exist),  and estimation of $\lfsr$ is more robust.

@@

\begin{figure}
\begin{center}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr_s_nn-1.pdf} 
\caption{Comparison of true and estimated $\lfsr$ when data are simulated with no point mass at zero ($\pi_0=0$), and also analyzed by \ashr with no point mass on 0 (and mixture of normal components for $g$). Black line is $y=x$ and red line is $y=2x$. The results illustrate how estimates of $\lfsr$ can be more accurate in this case. That is, assuming there is no point mass can be beneficial if that is indeed true.}  \label{fig:lfsr-nn}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr_s-1.pdf} 
\caption{Comparison of true and estimated $\lfsr$ when data are simulated with point mass at zero (drawn uniformly from [0,1] in each simulation), but analyzed by \ashr with no point mass on 0 (and mixture of normal components for $g$). Black line is $y=x$ and red line is $y=2x$. The results illustrate how estimates of $\lfsr$ can be anti-conservative if we assume there is no point mass when the truth is that there is a point mass.} \label{fig:lfsr-s}
\end{subfigure}
\end{center}
\caption{Illustration of effects of excluding a point mass from the analysis.} \label{fig:lfsr-nopointmass}
\end{figure}

>>>>

Our {\tt R} package implementation typically takes about $20$ seconds on a modern laptop for $p=100,000$, and scales linearly with $J$.

@@

\begin{figure} 
\begin{center}
\begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{../analysis/figure/plot_egdens.Rmd/scenario_density-1.pdf} 
	\caption{Densities of non-zero effects, $g_1$, used in simulations.} \label{fig:altdens}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_pi0est.Rmd/plot_pi0est-1.pdf} 
\caption{Comparison of true and estimated values of $\pi_0$. When the UA holds all methods yield conservative (over-)estimates for $\pi_0$, with \ashr being least conservative, and hence most accurate. When the UA does not hold (``bimodal" scenario) the \ashr estimates are slightly anti-conservative.} \label{fig:pi0sims}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfdr-1.png} 
\caption{Comparison of true and estimated $\lfdr$ from \ashr (ash.n). Black line is $y=x$ and red line is $y=2x$. Estimates of $\lfdr$ are conservative when UA holds, due to conservative estimates of $\pi_0$.} \label{fig:lfdr}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr-1.png} 
\caption{As in c), but for $\lfsr$ instead of $\lfdr$. Estimates of $\lfsr$ are consistently less conservative than $\lfdr$ when UA holds, and also less anti-conservative in bimodal scenario.}  \label{fig:lfsr}
\end{subfigure}
\end{center}
\caption{Results of simulation studies (constant precision $s_j=1$).}
\end{figure}

@@

Note that, compared with previous debates regarding testing, 
this section advances an additional reason for focussing on the sign of the effect, rather than just testing whether it is 0. 
In previous debates authors have argued against testing whether an effect is 0
because it is {\it implausible that effects are exactly 0}. Here we add that {\it even if one believes
that some effects may be exactly zero}, it is still better to focus on the sign, because generally {\it the data are more informative about that question}
and so inferences are more robust to, say, the inevitable mis-estimation of $\pi_0$.
To provide some intuition, consider an observation with a $z$ score of 0. The $\lfdr$ of this observation can range from 0 (if $\pi_0=0$)
to 1 (if $\pi_0=1$). But, assuming a symmetric $g$, the $\lfsr>0.5$ whatever the value of $\pi_0$, because the observation $z=0$ says
nothing about the sign of the effect.
Thus, there are two reasons to use the $\lfsr$ instead of the $\lfdr$: it answers a question that is more generally meaningful (e.g. it applies
whether or not zero effects truly exist),  and estimation of $\lfsr$ is more robust.

@@

\begin{figure}
\begin{center}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr_s_nn-1.png} 
\caption{Comparison of true and estimated $\lfsr$ when data are simulated with no point mass at zero ($\pi_0=0$), and also analyzed by \ashr with no point mass on 0 (and mixture of normal components for $g$). Black line is $y=x$ and red line is $y=2x$. The results illustrate how estimates of $\lfsr$ can be more accurate in this case. That is, assuming there is no point mass can be beneficial if that is indeed true.}  \label{fig:lfsr-nn}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr_s-1.png} 
\caption{Comparison of true and estimated $\lfsr$ when data are simulated with point mass at zero (drawn uniformly from [0,1] in each simulation), but analyzed by \ashr with no point mass on 0 (and mixture of normal components for $g$). Black line is $y=x$ and red line is $y=2x$. The results illustrate how estimates of $\lfsr$ can be anti-conservative if we assume there is no point mass when the truth is that there is a point mass.} \label{fig:lfsr-s}
\end{subfigure}
\end{center}
\caption{Illustration of effects of excluding a point mass from the analysis.} \label{fig:lfsr-nopointmass}
\end{figure}
